Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-28 demystify.tex
updates

From my experience, this is \emph{not} a good idea and can be considered \emph{rude and unprofessional}. But ultimately, it is a trade-off that you need to decide,  e.g., between your own benefit and the cost to others. If you reject an offer, the prof. will likely stop looking for other students and might even reject other students; so by rejecting the offer later, you causing a great deal of inconvenience to the prof and also taking away the opportunity from other students. This will likely would burn bridges with that prof and they will remember what you did to them.  Moreover, given that research subfields are typically small, you might run into that professor again in the future, and they will remember what you did to them.

@@

Plagiarism and cheating (e.g., exams, assignments) are a BIG no-no in the US.  If you're caught cheating, you will face serious consequences and likely be expelled from the university (e.g., after the second time at GMU).   This is quite different from many international countries where cheating is common and often tolerated.  Faculty is extremely good at detecting cheating (we have been dealing with these situations so many times over so many years), and \emph{will} report cheating cases.  In short, whatever you do, don't cheat---not worth it.

@@

\section{Gifts}\label{sec:gifts} In many countries, it is customary to give professors gifts, often during holidays.  These gifts can be costly and profs. sometimes expected them. In the US, it is uncommon and perfectly OK to not to give gifts. \emph{However}, if you'd like to offer small souvenir-like tokens, it's a thoughtful gesture that's appreciated. Some professors proudly display their gifts, which can come from students and colleagues (e.g., when they travel to their home countries or conferences). In summary, small gifts are fine, but avoid anything that might make your professors uncomfortable.

\section{Relationships with your Profs.}
There's a misconception that in the US it's all business, with professors as bosses who pay students for their work, and you doing something nice implying you expect something in return. However, the reality is quite the opposite. While people can be straightforward, they are also friendly and informal. You can call your professor by their first name (\autoref{sec:address}), disagree with them and argue (and gain respect doing so), seek their help (even on personal matters), come to their houses for parties or gathering, and give them small thoughtful gifts that they put on their desks (\autoref{sec:gifts}).  Many students and professors maintain lifelong relationships, staying in touch through cards, emails, and calls, even after their academic journey ends. %These connections are genuine and meaningful.

>>>>

From my experience, this is \emph{not} a good idea and can be considered \emph{rude and unprofessional}. But ultimately, it is a trade-off that you need to decide,  e.g., between your own benefit and the cost to others. If you reject an offer, the prof. will likely stop looking for other students and might even reject other students; so by rejecting the offer later, causing a great deal of inconvenience to the prof and also taking away the opportunity from other students. This will likely would burn bridges with that prof and they will remember what you did to them.  Moreover, given that research subfields are typically small, you might run into that professor again in the future, and they will remember what you did to them.

@@

Plagiarism and cheating (e.g., exams and assignments) are a BIG no-no in the US.  If you're caught cheating, you will face serious consequences and likely be expelled from the university (e.g., after the second time at GMU).   This is quite different from many international countries where cheating is common and often tolerated.  Faculty is extremely good at detecting cheating (we have been dealing with these situations so many times over so many years), and \emph{will} report cheating cases.  In short, whatever you do, don't cheat---not worth it.

@@

\section{Costly Gifts}\label{sec:gifts} In many countries, it is customary to give professors costly gifts (e.g., expensive liquors, jewelry, or even money), often during the holidays, to show respect and appreciation.  In the US, this is can be considered \emph{inappropriate} and discouraged.

However, if you'd like to offer small souvenir-like tokens, it's a thoughtful gesture that's appreciated. Some professors proudly display their gifts, which can come from students and colleagues (e.g., when they travel to their home countries or conferences). In summary, small gifts are fine, but avoid anything that might make your professors uncomfortable.

\section{Relationships}
There's a misconception that in the US it's all business, with professors as bosses who pay students for their work and that labmates are just work colleagues; and that doing nice things means expecting something in return.

However, the reality is quite the opposite. While people can be straightforward and appear ``cold'', they are also informal, friendly, and very caring (in ways that might surprise you).
With labmates and colleagues, you will often work and go to lunch together, confide in each other, help each other navigate the academic journey, and often become lifelong friends.
With your professor(s), you can call them by their first name (\autoref{sec:address}), disagree with them and argue (and gain respect doing so), seek their help (even on personal matters), come to their houses for parties or gathering, and give them small thoughtful gifts that they put on their desks (\autoref{sec:gifts}).  
Many people maintain lifelong relationships with their professors and colleagues, staying in touch through cards, emails, and calls, even after their academic journey ends. %These connections are genuine and meaningful.
